\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=1.75cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}

\definecolor{ink}{HTML}{1F2933}
\definecolor{muted}{HTML}{5F6B75}
\definecolor{accent}{HTML}{2F6F73}
\definecolor{rule}{HTML}{D8DEE4}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\emergencystretch}{3em}
\setlist[itemize]{leftmargin=1.2em,itemsep=2pt,topsep=2pt}
\setlist[enumerate]{leftmargin=1.4em,itemsep=3pt,topsep=3pt}

\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}
  {0pt}
  {}
  [\vspace{-4pt}{\color{rule}\titlerule}]

\newcommand{\cvsection}[1]{\section*{#1}}
\newcommand{\role}[4]{%
  \textbf{#2}\hfill{\color{muted}#1}\\
  \textit{#3}\\
  #4\par\vspace{3pt}
}
\newcommand{\degree}[4]{%
  \textbf{#2}\hfill{\color{muted}#1}\\
  \textit{#3}\\
  #4\par\vspace{3pt}
}
\newcommand{\paper}[4]{%
  \item \textbf{\href{#4}{#1}}. #2. \textit{#3}.
}
\newcommand{\paperplain}[3]{%
  \item \textbf{#1}. #2. \textit{#3}.
}

\begin{document}

{\Huge\bfseries Vasileios Sevetlidis}\\[3pt]
{\Large Machine Learning Researcher}\\[8pt]
\href{mailto:vasiseve@athenarc.gr}{vasiseve@athenarc.gr} \quad
\href{https://vasiseve.github.io}{vasiseve.github.io} \quad
\href{https://orcid.org/0000-0001-9348-8786}{ORCID: 0000-0001-9348-8786}\\
\href{https://scholar.google.com/citations?user=8RIQDfoAAAAJ&hl=en}{Google Scholar} \quad
\href{https://arxiv.org/search/cs?searchtype=author&query=Sevetlidis,+V}{arXiv} \quad
\href{https://github.com/vasiseve}{GitHub} \quad
\href{https://gitlab.com/vasiseve}{GitLab}

\vspace{8pt}

\cvsection{Profile}
I am a machine learning researcher studying how learning systems evolve over time. My research asks how models organize information, retain memory of training, and develop path-dependent behavior through optimization. I work at the intersection of geometry, dynamics, and statistical learning, with interests in weak supervision, positive-unlabeled learning, representation geometry, training memory, and diffusion models.

More broadly, I see machine learning as a dynamical process whose behavior cannot be understood only through final performance. I am interested in how representations form, how optimization preserves traces of history, and how generative models reflect the geometric structure of the fields they learn.

\cvsection{Research Interests}
\begin{itemize}
  \item Learning dynamics, optimizer memory, and path-dependent behavior in deep neural networks.
  \item Representation geometry, gauge-invariant diagnostics, holonomy, and geometric statistics for learned features.
  \item Positive-unlabeled learning, weak supervision, label bias, and learning from incomplete supervision.
  \item Dataset bias, anomaly-informed training, machine vision, and applied learning systems.
  \item Diffusion models, generative modeling, and geometry-aware diagnostics for sampling dynamics.
\end{itemize}

\cvsection{Current Positions}
\role{Feb 2025--present}{Adjunct Professor}{International Hellenic University}{Department of Computer, Informatics and Telecommunications Engineering.}
\role{Nov 2024--present}{Postdoctoral Researcher}{Democritus University of Thrace}{Automation and Robotics Laboratory, Department of Production and Management Engineering.}
\role{Jan 2019--present}{Research Associate}{Athena Research Center}{Collaboration with the Institute for Language and Speech Processing.}
\role{Jul 2022--present}{Freelance IT Engineer}{Independent practice}{Software, data, and machine-learning engineering work.}

\cvsection{Education}
\degree{2018--2024}{PhD, Production and Management Engineering}{Democritus University of Thrace}{Dissertation: \textit{Learning from positive and unlabeled data for imbalanced datasets: theory and real-world applications}.}
\degree{2016--2018}{MSc, Applied Archaeological Sciences}{University of the Aegean}{Graduated summa cum laude. Thesis: \textit{A Machine Learning Approach to Analysis and Classification of Measurements in Cultural Heritage}.}
\degree{2014--2016}{Doctoral Studies, Image Analysis}{IMT Institute for Advanced Studies Lucca}{Withdrew. Research topic: learning-based modality synthesis and normalization for cardiovascular magnetic resonance imaging.}
\degree{2008--2013}{BSc, Information and Communication Engineering}{TEI of Central Macedonia}{Graduated summa cum laude.}

\cvsection{Professional Experience}
\role{Jun 2019--Oct 2020}{Research Associate}{Foundation for Research and Technology - Hellas}{Collaboration with the Institute for Mediterranean Studies.}
\role{Nov 2015--Aug 2016}{Visiting Researcher}{University of Edinburgh}{Electrical Engineering; learning-based image modality synthesis.}
\role{Sep 2013--Aug 2014}{Research Associate}{Athena Research Center}{Collaboration with the Institute for Language and Speech Processing.}
\role{Feb 2013--Jun 2013}{Intern}{OTE S.A.}{Transmission and access network.}

\cvsection{Teaching}
\role{Feb 2025--Jun 2025; Feb 2026--Jun 2026}{Operating Systems I}{International Hellenic University}{Department of Computer, Informatics and Telecommunications Engineering.}
\role{Sep 2025--Jan 2026}{Operating Systems II}{International Hellenic University}{Department of Computer, Informatics and Telecommunications Engineering.}
\role{Sep 2025--Jan 2026}{Simulation and System Identification}{International Hellenic University}{Department of Computer, Informatics and Telecommunications Engineering.}

\cvsection{Selected Research Projects}
\begin{itemize}
  \item \textbf{\href{https://www.argus-project.eu}{ARGUS}} (2024): Non-destructive, scalable, smart monitoring of remote cultural treasures.
  \item \textbf{\href{https://firefly.athenarc.gr}{Firefly}} (2024): Fostering virtual heritage experience for elderly users.
  \item \textbf{\href{http://canti.athenarc.gr}{CAnTi}} (2022): Conservation of Ancient Tiryns.
  \item \textbf{\href{http://thalia.athenarc.gr}{Thalia}} (2022): Digital toolset for the analysis, promotion, and protection of Greek cultural reserves in small cultural institutions.
  \item \textbf{\href{https://tramir.bookscanner.gr}{Tramir}} (2022): Interactive music room for traditional Greek music instruments and dances.
  \item \textbf{\href{http://evrinomi.athenarc.gr}{Evrinomi}} (2022): Documentation and promotion of human creativity and culture at the Archaeological Museum of Patras.
  \item \textbf{\href{http://www.warmestproject.eu/}{WARMEST}} (2022): Remote sensing and integrated maintenance models for cultural heritage sites.
  \item \textbf{\href{http://philotis.athenarc.gr}{PHILOTIS}} (2020): Technologies for recording, analysis, and documentation of living languages.
  \item \textbf{\href{http://gre-taste.ceti.gr}{Gre-Taste}} (2019): AI and data systems for Greek gastronomy.
  \item \textbf{\href{https://politeia-ii.ims.forth.gr/vtms}{POLITEIA II}} (2019): Cultural heritage technology, documentation, and accessibility.
  \item \textbf{\href{http://advent.ceti.gr}{AdVENt}} (2019): Augmented tours in national parks.
  \item \textbf{\href{http://3dcms.ceti.gr}{3DCMS}} (2013): Platform for the development and management of 3D cultural heritage applications.
\end{itemize}

\cvsection{Awards and Scholarships}
\begin{itemize}
  \item Scholarship and distinction for graduating first in the MSc cohort, University of the Aegean, 2018.
  \item Erasmus+ Mobility Consortium for traineeships, ``Talent at Work'', 2015/2016.
  \item Italian Government scholarship for doctoral studies, 2014.
  \item Scholarship and distinction for graduating first, TEI of Central Macedonia, 2013.
\end{itemize}

\cvsection{Service}
\begin{itemize}
  \item Session Chair, International Conference on Pattern Recognition Applications and Methods.
  \item Program Committee, EETN Conference on Artificial Intelligence.
  \item Reviewer, International Conference on Machine Learning.
  \item Reviewer, Neural Information Processing Systems.
  \item Reviewer, International Journal of Computational Methods in Heritage Science.
  \item Reviewer, 5th CAA-GR Conference, Transforming Heritage Research in a Transforming World, 2024.
\end{itemize}

\cvsection{Publications}
\textbf{Learning dynamics, representation geometry, and training memory}
\begin{enumerate}
  \paper{Process-Tensor Tomography of SGD: Measuring Non-Markovian Memory via Back-Flow of Distinguishability}{V. Sevetlidis and G. Pavlidis}{AISTATS, 2026}{https://openreview.net/forum?id=TonOzlbE3k}
  \paper{Gauge-invariant representation holonomy}{V. Sevetlidis and G. Pavlidis}{ICLR, 2026}{https://openreview.net/forum?id=czJqKToDGq}
  \paper{Training Memory in Deep Neural Networks: Mechanisms, Evidence, and Measurement Gaps}{V. Sevetlidis and G. Pavlidis}{arXiv, 2026}{https://arxiv.org/abs/2601.21624}
\end{enumerate}

\textbf{Positive-unlabeled learning and weak supervision}
\begin{enumerate}
  \paper{Angular Regularization for Positive-Unlabeled Learning on the Hypersphere}{V. Sevetlidis, G. Pavlidis, and A. Gasteratos}{Transactions on Machine Learning Research, 2025}{https://openreview.net/forum?id=XQhO0Ly6el}
  \paper{Two-Stage Angular Alignment for Positive-Unlabeled Learning}{V. Sevetlidis, G. Pavlidis, and A. Gasteratos}{International Conference on Pattern Recognition Applications and Methods, 2026}{https://www.scitepress.org/Papers/2026/139641/139641.pdf}
  \paper{Dense-PU: Learning a Density-Based Boundary for Positive and Unlabeled Learning}{V. Sevetlidis, G. Pavlidis, S. G. Mouroutsos, and A. Gasteratos}{IEEE Access, 2024}{https://doi.org/10.1109/ACCESS.2024.3420453}
  \paper{Leveraging Positive-Unlabeled Learning for Enhanced Black Spot Accident Identification on Greek Road Networks}{V. Sevetlidis, G. Pavlidis, S. G. Mouroutsos, and A. Gasteratos}{Computers, 2024}{https://doi.org/10.3390/computers13020049}
  \paper{Positive and Unlabelled Learning with Data Approximation for Photovoltaic Defect Detection}{V. Sevetlidis, G. Pavlidis, S. G. Mouroutsos, T. Karakatsanis, and A. Gasteratos}{IEEE International Conference on Imaging Systems and Techniques, 2024}{https://doi.org/10.1109/IST63414.2024.10759214}
  \paper{Detecting Media Clones in Cultural Repositories Using a Positive Unlabeled Learning Approach}{V. Sevetlidis, V. Arampatzakis, M. Karta, I. Mourthos, D. Tsiafaki, and G. Pavlidis}{arXiv, 2026}{https://arxiv.org/abs/2604.04071}
  \paper{Learning from positive and unlabeled data for imbalanced datasets: theory and real-world applications}{V. Sevetlidis}{PhD thesis, Democritus University of Thrace, 2024}{https://repo.lib.duth.gr/jspui/handle/123456789/19964}
  \paper{Enhancing Weakly Supervised Defect Detection Through Anomaly-Informed Weighted Training}{V. Sevetlidis, G. Pavlidis, V. Balaska, A. Psomoulis, S. G. Mouroutsos, and A. Gasteratos}{IEEE Transactions on Instrumentation and Measurement, 2024}{https://ieeexplore.ieee.org/document/10716729/}
  \paper{Defect Detection Using Weakly Supervised Learning}{V. Sevetlidis, G. Pavlidis, V. Balaska, A. Psomoulis, S. Mouroutsos, and A. Gasteratos}{IEEE International Conference on Imaging Systems and Techniques, 2023}{https://arxiv.org/abs/2303.15092}
\end{enumerate}

\textbf{Dataset bias, applied machine learning, and machine vision}
\begin{enumerate}
  \paper{Machine Vision in Human-Centric Manufacturing: A Review from the Perspective of the Frozen Dough Industry}{V. Balaska, A. Tserkezis, F. Konstantinidis, V. Sevetlidis, S. Symeonidis, T. Karakatsanis, and A. Gasteratos}{Electronics, 2025}{https://doi.org/10.3390/electronics14173361}
  \paper{Deep Learning-Based Black Spot Identification on Greek Road Networks}{I. Karamanlis, A. Kokkalis, V. Profillidis, G. Botzoris, C. Kiourt, V. Sevetlidis, and G. Pavlidis}{Data, 2023}{https://doi.org/10.3390/data8060110}
  \paper{Tackling Dataset Bias With an Automated Collection of Real-World Samples}{V. Sevetlidis, G. Pavlidis, S. Mouroutsos, and A. Gasteratos}{IEEE Access, 2022}{https://doi.org/10.1109/ACCESS.2022.3226517}
  \paper{Web Acquired Image Datasets Need Curation: An Exemplar Pipeline Evaluated on Greek Food Images}{V. Sevetlidis, G. Pavlidis, V. Arampatzakis, C. Kiourt, S. G. Mouroutsos, and A. Gasteratos}{IEEE International Conference on Imaging Systems and Techniques, 2021}{https://ieeexplore.ieee.org/abstract/document/9651419}
  \paperplain{AUGMENTING EXISTING FOOD IMAGE DATASETS WITH GREEK DISHES}{V. Sevetlidis, C. Kiourt, C. Tzouvara, G. Tastzoglou, and G. Pavlidis}{Big Data in Archaeology, 2021}
  \paper{Whole Image Synthesis Using a Deep Encoder-Decoder Network}{V. Sevetlidis, M. V. Giuffrida, and S. A. Tsaftaris}{Simulation and Synthesis in Medical Imaging, MICCAI workshop, 2016}{https://doi.org/10.1007/978-3-319-46630-9_13}
  \paper{BK Tree Indexing for Active Vision-Based Loop-Closure Detection in Autonomous Navigation}{K. A. Tsintotas, V. Sevetlidis, I. T. Papapetros, V. Balaska, A. Psomoulis, and A. Gasteratos}{Mediterranean Conference on Control and Automation, 2022}{https://ieeexplore.ieee.org/document/9837138/}
  \paper{Shaping the Behavior of Reinforcement Learning Agents}{G. Sidiropoulos, C. Kiourt, V. Sevetlidis, and G. Pavlidis}{Pan-Hellenic Conference on Informatics, 2021}{https://doi.org/10.1145/3503823.3503905}
\end{enumerate}

\textbf{Cultural heritage, digital twins, and scientific measurements}
\begin{enumerate}
  \paper{PANOPTES: A Digital Twin Ontology for Cultural Asset Management}{G. Pavlidis, V. Sevetlidis, and V. Arampatzakis}{IEEE-CH, 2025}{https://doi.org/10.5281/zenodo.16633603}
  \paper{Defining a New Digital Twin Ontology for Cultural Heritage Preservation - the Case of ARGUS}{G. Pavlidis, V. Sevetlidis, and V. Arampatzakis}{Eurographics, 2025}{https://zenodo.org/records/17276771}
  \paper{Towards Evolving Actor-Network Ontologies: Enabling Reflexive Digital Twins for Cultural Heritage}{G. Pavlidis, V. Arampatzakis, V. Sevetlidis, A. Koutsoudis, F. Arnaoutoglou, G. A. Ioannakis, and C. Kiourt}{Information, 2025}{https://doi.org/10.3390/info16100892}
  \paper{Future-Proofing Heritage with ARGUS: A Multimodal Digital Twin Approach for Sustainable Preservation}{G. Pavlidis, A. Koutsoudis, D. Tsiafakis, M. Karta, V. Sevetlidis, and others}{CAA Proceedings, 2025}{https://doi.org/10.5281/zenodo.17755550}
  \paper{Sensor-Driven Preventive Preservation in Remote Built Heritage: A Threat-to-Sensor Approach}{G. Pavlidis, V. Sevetlidis, V. Arampatzakis, S. Aparicio, F. Ramonet, and others}{IEEE-CH, 2025}{https://ieeexplore.ieee.org/abstract/document/11279543}
  \paper{Towards Complete Digital Twins in Cultural Heritage with ART3mis 3D Artifacts Annotator}{D. Karamatskos, V. Arampatzakis, V. Sevetlidis, S. Nousias, A. Kalogeras, and others}{arXiv, 2026}{https://arxiv.org/abs/2602.12761}
  \paper{Art3mis: Ray-Based Textual Annotation on 3D Cultural Objects}{V. Arampatzakis, V. Sevetlidis, F. Arnaoutoglou, A. Kalogeras, C. Koulamas, and others}{arXiv, 2026}{https://arxiv.org/abs/2602.12725}
  \paper{Museatopia: A Cultural Metaverse}{V. Arampatzakis, H. G. Theodoropoulou, C. Kiourt, V. Sevetlidis, and G. Pavlidis}{CAA-GR, 2026}{https://doi.org/10.1007/978-3-032-06389-2_18}
  \paper{Effective Raman Spectra Identification with Tree-Based Methods}{V. Sevetlidis and G. Pavlidis}{Journal of Cultural Heritage, 2019}{https://doi.org/10.1016/j.culher.2018.10.016}
  \paper{Hierarchical Classification for Improved Compound Identification in Raman Spectroscopy}{V. Sevetlidis and G. Pavlidis}{CAA-GR, 2018}{https://sites.caa-international.org/gr/wp-content/uploads/sites/26/2019/04/CAA-GR-2018-proceedings.pdf}
  \paper{A Machine Learning Approach to Analysis and Classification of Measurements in Cultural Heritage}{V. Sevetlidis}{MSc thesis, University of the Aegean, 2018}{https://www.openarchives.gr/aggregator-openarchives/edm/hellanicus/000100-11610_19962?language=en}
  \paper{Efficient Colour Sorting of Chios Mastiha}{G. Pavlidis, S. Mouroutsos, and V. Sevetlidis}{IEEE International Conference on Imaging Systems and Techniques, 2014}{https://ieeexplore.ieee.org/abstract/document/6958510}
  \paper{Sustainability through Digital Transition: The Case of Small Cultural Stakeholders}{G. Pavlidis, S. Markantonatou, K. Chairi, V. Sevetlidis, V. Arampatzakis, and others}{Conference proceedings, 2024}{https://doi.org/10.12681/elrie.7138}
  \paper{Demystifying Publishing to Europeana: A Practical Workflow for Content Providers}{G. Pavlidis and V. Sevetlidis}{Scientific Culture, 2015}{https://www.sci-cult.com/demystifying-publishing-to-europeana-a-practical-workflow-for-content-providers/}
\end{enumerate}

\textbf{Language technology, human-centric interaction, and society}
\begin{enumerate}
  \paper{ASR Pipeline for Low-Resourced Languages: A Case Study on Pomak}{C. Tsoukala, K. Kritsis, I. Douros, A. Katsamanis, N. Kokkas, V. Arampatzakis, V. Sevetlidis, S. Markantonatou, and G. Pavlidis}{NLP Applications to Field Linguistics, 2023}{https://aclanthology.org/2023.fieldmatters-1.5/}
  \paper{Morphologically Annotated Corpora of Pomak}{R. J. Karahoga, P. G. Krimpas, V. Stamou, V. Arampatzakis, D. Karamatskos, V. Sevetlidis, and S. Markantonatou}{Computational Methods in the Study of Endangered Languages, 2022}{https://aclanthology.org/2022.computel-1.22/}
  \paper{Philotis: NLP Informed Language Documentation of Under-Resourced Languages - The Case of Pomak}{V. Stamou, V. Arampatzakis, N. Constantinides, N. Kokkas, D. Karamatskos, V. Sevetlidis, and others}{HCSTG, 2022}{https://doi.org/10.5281/zenodo.7598116}
  \paper{Human-Centric Emotion Recognition in VR for Humanities Research}{V. Sevetlidis, V. Arampatzakis, G. Pavlidis, and S. Sylaiou}{CAA-GR, 2026}{https://doi.org/10.1007/978-3-032-06389-2_21}
  \paper{Towards Reshaping Children's Habits: Vitalia's AR-Gamified Approach}{V. Arampatzakis, V. Sevetlidis, V. Derri, M. Raffi, and G. Pavlidis}{Information, 2025}{https://doi.org/10.3390/info16070606}
  \paper{Sustainable Ecotourism through Cutting-Edge Technologies}{G. Pavlidis, A. Solomou, S. Stamouli, V. Papavassiliou, K. Kritsis, C. Kiourt, V. Sevetlidis, and others}{Sustainability, 2022}{https://doi.org/10.3390/su14020800}
  \paper{GRASP-125: A Dataset for Greek Vascular Plant Recognition in Natural Environment}{K. Kritsis, C. Kiourt, S. Stamouli, V. Sevetlidis, A. Solomou, G. Karetsos, and others}{Sustainability, 2021}{https://doi.org/10.3390/su132111865}
  \paper{AI in Gastronomic Tourism}{G. Pavlidis, S. L. Markantonatou, K. R. Toraki, A. N. Vacalopoulou, and others}{Signal Processing and Information Technology, 2020}{https://doi.org/10.5281/zenodo.3862543}
\end{enumerate}

\cvsection{Technical Reports and Theses}
\begin{itemize}
  \item V. Sevetlidis. \textit{Learning from positive and unlabeled data for imbalanced datasets: theory and real-world applications}. PhD dissertation, Democritus University of Thrace, 2024.
  \item V. Sevetlidis. \textit{A Machine Learning Approach to Analysis and Classification of Measurements in Cultural Heritage}. MSc thesis, University of the Aegean, 2018.
  \item V. Sevetlidis. \textit{Analysis of Color Images for Colour Based Image Retrieval Applications}. BSc thesis, TEI of Central Macedonia, 2013.
  \item G. Pavlidis, V. Sevetlidis, and M. Charalampidou. \textit{Improvement of Digitization and Modeling Methods}. Technical report, 2014.
  \item G. Pavlidis, V. Sevetlidis, and M. Charalampidou. \textit{Methods for 3D Digitization of Objects and Monuments}. Technical report, 2014.
  \item G. Pavlidis and V. Sevetlidis. \textit{Europeana Connectivity Study}. Technical report, 2014.
  \item G. Pavlidis and V. Sevetlidis. \textit{Documentation Schemas for Museums and 3D Objects}. Technical report, 2014.
  \item G. Pavlidis and V. Sevetlidis. \textit{Competitive Related Products}. Technical report, 2013.
\end{itemize}

\cvsection{Languages, Certificates, and Activities}
\begin{itemize}
  \item Languages: Greek (native), English (B2), Italian (basic).
  \item Certified UAS pilot, open category, 2020.
  \item Introduction to Grid Computing, SURFSara, Dutch HPC and e-Science, 2014.
  \item Fiber Optics Association certification, 2012.
  \item Open-sea sailing license, 2019.
  \item Photography exhibitions and competitions, 2013--present.
\end{itemize}

\end{document}
